---
title: "Disparities in Obesity and Risk of Breast Cancer across Racial/Ethnic Groups in the United States, Using NHANES 2011-16 Datasets"
author: Sha Tao (st3117), Jingqi Song (js5165), Yixuan Wang (yw3095),  Ditian Li (dl3157),  Boya Guo (bg2604)
date: "December 6, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
library(httr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_bw())
```

###Motivation 

Breast cancer is the most commonly diagnosed cancer among American women. It is estimated that about 1 in 8 U.S women will develop invasive breast cancer over the course of lifetime.  An inverse association between obesity and breast cancer has been reported by many studies. Previous studies have also found the age-adjusted ethnic difference in breast cancer incidence rates. Despite this disparity, the influence of obesity as a breast cancer risk factor on differences in incidence associated with ethnicity/race has received limited attention. The objective of this project is to investigate whether the impact of obesity on breast cancer varies across racial/ethnic groups from 2011 to 2016 in the United States. 

###Related work


###Initial Questions:

Are there Disparities in obesity and risk of breast cancer across racial/ethnic groups in the United States, when controlling for age?

###Data

**Source**
We are going to use the Demographics, Examination Data and Dietary Data from NHANES 2011-2016 datasets. NHANES is a nationally representative, multi-stage complex survey designed to assess the health and nutritional status of the non-institutionalized, civilian US population. https://wwwn.cdc.gov/nchs/nhanes/Default.aspx

**Scraping Method**
We cleaned our data from NHANES website from year 2011-2016, first we imported several questionnaire data and created data combination function. Then we chose and clean variables from each dataset, replaced the missing value and selected the interest predictors and exposures.






* Establish a model representing the relationship between breast cancer and interested predictors race, age, weight, overweight.
** Visualization 



### Intended final products
We plan to present our project using the format of website and narrated screencast. In addition, we will create graphs, charts and/or Infographic and post them on our website. 

### Anticipated data sources
We are going to use the Demographics, Examination Data and Dietary Data from NHANES 2011-2016 datasets. NHANES is a nationally representative, multi-stage complex survey designed to assess the health and nutritional status of the non-institutionalized, civilian US population. https://wwwn.cdc.gov/nchs/nhanes/Default.aspx

### Planned analyses / visualizations / coding challenges
* Planned analyses
    + Analyze the age onset of breast cancer across the total population, and the distribution of obesity incidences across racial/ethnic groups
    + Use logistic regression to investigate the association between obesity and breast cancer in each race/ethnic groups 
* Visualizations
    + Boxplot of breast cancer incidences across racial/ethnic groups
    + Histogram of breast cancer incidences in each age groups
    + Scatter plot of breast cancer incidences in each racial/ethnic group across 6 years
* Coding challenges
    + In order to calculate the most accurate measure, we should use weighted analyses for complex survey design such as NHANES datasets. We expect there will be coding challenges regarding how to perform weighted analyses.
    + Perform logistic regression

### Planned timeline
We plan to meet on a weekly basis to discuss the project progress, and will follow the timeline below:
```{r timeline, echo = FALSE, message = FALSE}

read_csv("./data/time_line.csv") %>% knitr::kable()

```

### References
1. Bandera, Elisa V., et al. "Racial and Ethnic Disparities in the Impact of Obesity on Breast Cancer Risk and Survival: A Global Perspective–." *Advances in Nutrition 6.6 (2015): 803-819.* https://academic.oup.com/advances/article/6/6/803/4555151
2. Chlebowski, Rowan T., et al. "Ethnicity and breast cancer: factors influencing differences in incidence and outcome." *Journal of the National Cancer Institute 97.6 (2005): 439-448.* https://academic.oup.com/jnci/article/97/6/439/2544155
3. Picon‐Ruiz, Manuel, et al. "Obesity and adverse breast cancer risk and outcome: mechanistic insights and strategies for intervention." *CA: a cancer journal for clinicians 67.5 (2017): 378-397.* https://onlinelibrary.wiley.com/doi/full/10.3322/caac.21405